Put Title here

### 2018-06-21 General WLD combinatorics.tex
minor things

These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$. The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 times 1$ minors of $C(W)$ as defined below.

\begin{dfn}
For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it. For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$. Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}{s-1} \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $s = 1$, $R_e = c_{p,e} c_{p,e+1}$.
\end{dfn}

@@

A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite, face are triangles.

@@

\begin{cor}
  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.  Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
  \[
  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2}
  \]
\end{cor}

@@

Define $b_1 = \min{k_1+1, s_1+1}$. We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$. (If $b_1 <_{j+1} i+2$ then this interval is empty.) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}. Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $b_1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range. If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$. In this case, we say $b_1= j$.

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix \hlfix{which has some actual name and a ref to where you define it}.
\begin{itemize}
  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
    \begin{itemize}
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous as is each $r_i$.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item $R$ is the radical of $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.  Therefore $R$ is the radical of $\prod_{i=1}^n \Delta_{I_i}$.
  \end{enumerate}
\end{proof}

\begin{thm}\label{thm denom}
Given any admissible Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral $I(W)$ is the \hlfix{find correct word for this} is the minimal polynomial of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
\end{thm}

>>>>

These $C(W)$ parametrize a subspace of $\Gr(k, n)$ as shown in \cite{wilsonloops}, call it $\Sigma(W)$. The Wilson loop diagrams also define a volume form on $\Sigma(W)$: \bas \Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V_{p_r}} \textrm{d}c_{p_r}}{R(W)} \;. \eas The denominator $R(W)$ is a polynomial defined by $2 \times 2$ and $1 \times 1$ minors of $C(W)$ as defined below.

\begin{dfn}\label{def R(W)}
For $W = (\cP, n)$, $R(W) = \prod_{e=1}^n R_e$, with $R_e$ defined by the propagators ending on it. For any edge $e$ of $W$, order the propagators incident on $e$ as $\{p_1 \ldots p_r\}$, ordered such that $p_1$ is closest to the vertex $e$, $p_r$ closest to $e+1$, and $p_i$ is closer to $e$ than $p_{i+1}$. Then \bas R_e =  c_{p_1,e+1} \prod_{j= 1}(r-1) \left((c_{p_j,e} c_{p_{j+1},e+1} - c_{p_{j+1},e} c_{p_{j},e+1} ) \right) c_{p_s,e}\;.\eas Note that in this notation, if $r = 1$, $R_e = c_{p,e} c_{p,e+1}$.
\end{dfn}

@@

A planar embedding of a graph is a \emph{triangulation} if all faces, except possibly the infinite face, are triangles.

@@

\begin{cor}
  Let $W$ be an admissible Wilson loop diagram where the sizes of the supports of the nontrivial maximal connected exact subdiagrams are $n_1, n_2, \ldots, n_j$.  Then the number of admissible Wilson loop diagrams equivalent to $W$ (including $W$ itself) is
  \[
  \prod_{i=1}^{j} \frac{1}{n_i-1}\binom{2(n_i-2)}{n_i-2}
  \]
\end{cor}

@@

Define $b_1 = \min\{k_1+1, s_1+1\}$. We see that, if $r >0$, for all $a \in [i+2, b_1]$, $p$ contributes $j$ to $I_a$. (If $b_1 <_{j+1} i+2$ then this interval is empty.) This is because in this range, $j$ is the first vertex of $p$ encountered by Algorithm \ref{Alg: put GN on WLD}. Furthermore, by Lemma \ref{protect conv lem}, and definition \ref{protect dfn} if $b_1 \not <_{j+1} i+2$ $P_1$ does not protect $p$ at $j$ for $a$ in this range. If $r = 0$ then $p$ contributes $j$ for all $a \in [i+2, j]$. In this case, we say $b_1= j$.

@@

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W$ be a Wilson loop diagram with $n$ vertices.  Let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn}.
\begin{itemize}
  \item For each $i \in \interval{1}{n}$, we construct a factor $r_i$ as follows
    \begin{itemize}
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i$ be the set of propagators $p$ such that $I_{i-1}(p) \neq I_{i}(p)$.
      \item $\Delta_{I_i}$ is the determinant of the $k \times k$ minor of $C(W)$ indicated by $I_i$.
      \item Let $r_i$ be $\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

\begin{prop}\label{prop alg gives rad}
  With notation as in Algorithm~\ref{alg WLD to denom via GN} we have the following:
  \begin{enumerate}
    \item Each $\Delta_{I_i}$ is homogeneous as is each $r_i$.
    \item Each $\Delta_{I_i}$ splits into linear and quadratic factors.  All linear factors of  $\Delta_{I_i}$ are single variables and all irreducible quadratic factors are $2\times 2$ determinants of single variables.
    \item Quadratic factors in $r_i$ arise precisely when propagators $p$ and $q$ are supported on a common edge $(a,b)$ and $I_i(p)=a$, $I_i(q)=b$.
    \item $r_i$ divides $\Delta_{I_i}$.
    \item The ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^{n}\Delta_{I_i}$.
  \end{enumerate}
\end{prop}

@@

Taking everything together we have that $R|\prod_{i=1}^n \Delta_{I_i}$, $R$ contains all factors of $\prod_{i=1}^n \Delta_{I_i}$ and $R$ is squarefree.  Therefore the ideal generated by $R$ is the radical of the ideal generated by $\prod_{i=1}^n \Delta_{I_i}$.
  \end{enumerate}
\end{proof}

\begin{thm}\label{thm denom}
Given any admissible Wilson loop diagram $W$, let $GN(W) = \{I_1, \ldots I_n\}$ be the associated Grasmann necklace. Then the denominator of the integral, $R(W)$ (see Definition~\ref{def R(W)}), is an integer multiple of the radical of $\prod_{i=1}^n \Delta_{I_i}$, where $\Delta_{I_i}$ is the determinant of the $k \times k$ minor indicated by $I_i$.
\end{thm}
